\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-07-14 foci/paper.tex
more edits

\title{\Large \bf Security Audit of Safeplug ``Tor in a Box''}
\author{
 {\rm Anne Edmundson}\\
 Princeton University
 \and
 {\rm Anna Kornfeld Simpson}\\
 Princeton University
 \and
 {\rm Joshua Kroll}\\
 Princeton University
 \and
 {\rm Edward Felten}\\
 Princeton University
} % end author

@@

\begin{itemize} %\setlength{\itemsep}{2mm}
\item Plain Firefox (no use of the Safeplug device)
\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
\item Firefox, Tor, no ad-blocking
\item Firefox, Tor, ad-blocking
\item Firefox, no Tor, ad-blocking
\item Tor Browser Bundle with Safeplug (all settings off)
\item Tor Browser Bundle
\end{itemize}

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  A differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.  We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.  Because measuring privacy is a difficult task, we measured potential ways for a user's privacy to be compromised.  First, we recorded how many third party domains were accessed per page; this is shown in the second column of Table \ref{tbb}.  The third and fourth columns show the number of JavaScript objects and the number of Flash objects received from third parties per page, respectively.  Lastly, we kept track of the number of third party cookies received per page, and this is seen in the last column.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the fraction of Third Party Domains accessed per page, Javascript objects received from third parties per page, the number of Flash objects received from third parties per page, and the number of third party cookies received per page.}
\label{tbb}
\centering
\small
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & JavaScript & Flash & Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\end{table}

@@

\section{Future Work}
A more in-depth analysis of the performance of the Safeplug would be useful in the future.  The performance of the Safeplug reflects it's usability, and would be helpful in determining the trade-offs of using the device.  Additionally, a greater breadth of privacy measurements would cement Safeplug's position as a useful privacy-preserving technology, or a device that doesn't protect privacy as well as other tools.

>>>>

\title{\Large \bf Security Audit of Safeplug ``Tor in a Box''}
\author{
 {\rm Anne Edmundson}\\
 Princeton University
 \and
 {\rm Anna Kornfeld Simpson}\\
 Princeton University
 \and
 {\rm Joshua A. Kroll}\\
 Princeton University
 \and
 {\rm Edward W. Felten}\\
 Princeton University
} % end author

@@

\begin{itemize} %\setlength{\itemsep}{2mm}
\item Plain Firefox (no use of the Safeplug device)
\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
\item Firefox, Tor, no ad-blocking (using the Safeplug device)
\item Firefox, Tor, ad-blocking (using the Safeplug device)
\item Firefox, no Tor, ad-blocking (using the Safeplug device)
\item Tor Browser Bundle with Safeplug (all settings off)
\item Tor Browser Bundle (no use of the Safeplug device)
\end{itemize}

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  A differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.  We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.  Because measuring privacy is a difficult task, we measured potential ways for a user's privacy to be compromised.  First, we recorded how many third party domains were accessed total (throughout the crawl); in addition, we recorded the total number of JavaScript and Flash objects received from third parties, as well as the total number of third party cookies received.  We then found the on-average, per-page numbers corresponding to these measurements by dividing the totals by 100.  These fractions are shown in Table~\ref{tbb}.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number of Third Party Domains accessed per page, the average number of Javascript objects received from third parties per page, the average number of Flash objects received from third parties per page, and the average number of third party cookies received per page.}
\label{tbb}
\centering
\small
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & JavaScript & Flash & Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\end{table}

@@

\section{Future Work}
A more in-depth analysis of the performance of the Safeplug would be useful in the future.  The performance of the Safeplug reflects its usability, and would be helpful in determining the trade-offs of using the device.  Additionally, clearer privacy metrics are needed to help evaluate privacy-enhancing technologies, such as the Safeplug.
